Empirical study of land surface effects on local rainfall

### 2017-11-08 LandSurfaceEffects_LocalRainfall_ClimDynsubmit.Rnw
add files

\documentclass[authoryear,preprint,review,12pt]{elsarticle}

\journal{Agriculture and Forest Meteorology}

\usepackage{url}
% Elsevier suggests
\usepackage{amssymb}
 \usepackage{lineno}

% older suggested by Chun
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{rotating}
\usepackage{bm}
% french characters
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%switch on line numbers
\linenumbers

\begin{document}
\SweaveOpts{concordance=TRUE}
\begin{frontmatter}

@@

\author{C. Liang}
\author{R.W. Vervoort \corref{cor1}}
\ead{willem.vervoort@sydney.edu.au}
\author{F.F. Van Ogtrop}

\address{Sydney Institute of Agriculture, School of Life and Environmental Sciences, The University of Sydney}
\cortext[cor1]{}

\begin{itemize}
\item There are limited studies that analyse observational data of vegetation feedback on rainfall
\item Two sites with major step trend landuse change were analysed for changes in rainfall
\item Statistical change in rainfall detected after bushfire, but not after land clearing
\end{itemize}

\begin{abstract}
Analysis of observational data to identify relationships between rainfall and land cover change are scarce due to multiple environmental factors that cannot be controlled. In this study we investigated the relationship using statistical methods on data from best available sources at two sites in Australia. Gridded data of rainfall and tree cover were used as spatially corresponding local conditions. Large scale effects were represented by climatic indicators, such as SOI and IOD. Regression analysis and step trend tests were used to assess the effect of abrupt land surface intervention. At a Queensland site, dramatic tree cover change between 2002 - 2005 did not result in strong statistically significant precipitation changes. On the other hand, results from step trend test on 1998 - 2008 rainfall data in a bushfire affected NSW/VIC region has a better match with the tree cover change map. This indicates the method works better when a abrupt change in the data can be clearly identified. The results from the step trend test implied a positive relationship between the tree cover and the rainfall at 0.1 significance level. 
\end{abstract}

\begin{keyword}
Observed data analysis \sep Rainfall change \sep Landcover feedback
\end{keyword}

\end{frontmatter}

@@

Overall the number of observational data studies related to changes to rainfall due to land cover change is limited. This is because there are some fundamental experimental difficulties in both space (where does evaporated water reappear as rainfall?) and in time (how much time does it take for land cover change effects to appear or disappear?). Therefore, the aim of this study is to use observational data at regional scales to investigate the cause and effect relationship between land cover change and local rainfall using empirical evidence. More specifically, we hypothesize that a step change on the land cover on the surface will cause a step change in the rainfall and that this can be identified statistically. To demonstrate the approach and this effect we studied step changes in rainfall at two locations in Queensland and NSW/Victoria where there are possible step changes in land cover change due to land clearing and bushfires based on tree cover data. More specifically,  step changes in rainfall were identified statistically, which were subsequently associated with land cover change through spatial comparison.

@@

In the first method, the tree cover change was used as a predictor in the regression model, represented by a factor variable \textbf{LC}. The significance of the coefficient of \textbf{LC}, denoted as $\beta'_2$ in Equation~\ref{eqn:model2}, can be determined by a ratio test.
\begin{linenomath*}
  \begin{equation}
    \mbox{LC} = \left\{ \begin{array}{ll}
       \mbox{Trees} \\
       \mbox{Removed}
    \end{array} \right.
    \label{eqn:dummyC}
  \end{equation}
\end{linenomath*}
Therefore in both regions, land cover is ``trees" for the period before land cover change and ``removed" for the period after the change. Here we simply assumed that vegetation cover change has occurred on every pixel. The remaining term $\epsilon_r$ is the amount of rainfall that is attributed to other unspecified factors and random errors. Hence the regression model becomes
\vspace{0.5cm}
%\begin{dmath}
\begin{linenomath*}
\begin{equation}
g(E(\mathbf{R}_r)) = \beta'_0 + s'_1(D_{1,r}\mathbf{SOI}) + s'_2(D_{2,r}\mathbf{IOD}) + s'_3\mathbf{Season} + \beta'_1\mathbf{Trend} + \beta'_2\mathbf{LC} + \boldsymbol{\epsilon'}_r
  \label{eqn:model2}
\end{equation}
\end{linenomath*}

Vegetation cover changes occurred at different times in the two regions. In the QLD region, there no exact time can be assigned to the land clearing. Clearing has occurred between 2003 - 2004 according to SLATS reports. The information on the change in type of land cover during this time period is missing. Therefore, four scenarios were tested in the analysis. In these scenarios the ``after change" period started from: (1) June 2003, (2) January 2004, (3) June 2004 and (4) January 2005. In the NSW/VIC region, severe bushfires were reported in early January 2003. Hence the ``tree" cover state was up to December 2002 then it was changed to ``removed" state from January 2003. The regression model was run from 1979 for both regions.

@@

The regression model used here is a simple model. We only consider the important effects of historical trend, seasonality and climate drivers. Furthermore, no more than two large scale climatic indices were used in order to avoid over-parameterisation and multiple cross-correlations between climatic indices. A purpose of the regression model is to remove the variability in rainfall that is due to these known important factors. The model shows that seasonality, ENSO and IOD together explain no more than 20\% of the rainfall variability, and around 6 - 8\% on average is due to the climate drivers. This is consistent with the literature \citep[e.g.][]{Westra2010}. A large amount of variation is left in the model residuals, which is likely due to random factors. Rainfall is generally considered a stochastic process \citep[e.g.][]{Fowler2005,Cowpertwait2009,Burton2010}. The high variability increases the difficulty to detect a change in rainfall.

@@

\newpage

%\bibliography
\bibliographystyle{elsarticle-harv} 
\bibliography{reflist_chap3}

>>>>

\RequirePackage{fix-cm}

\documentclass[onecolumn,referee]{svjour3}
\journalname{Climate Dynamics}

\usepackage{url}
% Springer suggests
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{spbasic} 
\usepackage{lineno}

% older suggested by Chun
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{rotating}
\usepackage{bm}
% french characters
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\linenumbers

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\author{C. Liang \and R.W. Vervoort \and F.F. Van Ogtrop}

\institute{C.Liang \at Sydney Institute of Agriculture, School of Life and Environmental Sciences, The University of Sydney \\
  \email{summer.chunliang@gmail.com}
  \and
  R.W. Vervoort \at Sydney Institute of Agriculture, School of Life and Environmental Sciences, The University of Sydney \\
  Tel: +61 86271054 \\
  \email{willem.vervoort@sydney.edu.au}
   \and
   F.F. van Ogtrop \at Sydney Institute of Agriculture, School of Life and Environmental Sciences, The University of Sydney \\
            \email{F.vanogtrop@sydney.edu.au}}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Analysis of observational data to identify relationships between rainfall and land cover change are scarce due to multiple environmental factors that cannot be controlled. In this study we investigated the relationship using statistical methods on data from best available sources at two sites (approx 306 by 274 km in Queensland) and approx 203 by 175 km in NSW) in Australia. Gridded data of rainfall and tree cover were used as spatially corresponding local conditions. Large scale effects affecting the regional space were represented by climatic indicators, such as SOI and IOD. Regression analysis and step trend tests were used to assess the effect of abrupt land surface intervention. At a Queensland site, dramatic tree cover change between 2002 - 2005 did not result in strong statistically significant precipitation changes. On the other hand, results from step trend test on 1998 - 2008 rainfall data in a bushfire affected NSW/VIC region has a better match with the tree cover change map. This indicates the method works better when a abrupt change in the data can be clearly identified. The results from the step trend test implied a positive relationship between the tree cover and the rainfall at 0.1 significance level. 
\end{abstract}

\keywords{Observed data analysis \and Rainfall change \and Landcover feedback}

@@

Overall the number of observational data studies related to changes to rainfall due to land cover change is limited. This is because there are some fundamental experimental difficulties in both space (where does evaporated water reappear as rainfall?) and in time (how much time does it take for land cover change effects to appear or disappear?). This might explain why modelling is mostly used to be able to deal with both the convergent and divergent nature of the regional process \citep{CEBON2000211}. Therefore, the aim of this study is to use observational data at regional scales to investigate the cause and effect relationship between land cover change and local rainfall. More specifically, we hypothesize that a step change on the land cover on the surface will cause a step change in the rainfall and that this can be identified statistically. To demonstrate the approach and this effect we studied step changes in rainfall at two locations in Queensland and NSW/Victoria where there are possible step changes in land cover change due to land clearing and bushfires based on tree cover data. More specifically,  step changes in rainfall were identified statistically, which were subsequently associated with land cover change through spatial comparison.

@@

In the first method, the tree cover change was used as a predictor in the regression model, represented by a factor variable \textbf{LC}. The significance of the coefficient of \textbf{LC}, denoted as $\beta'_2$ in Equation~\ref{eqn:model2}, can be determined by a ratio test.
\begin{linenomath*}
  \begin{equation}
    \mbox{LC} = \left\{ \begin{array}{ll}
       \mbox{Trees} \\
       \mbox{Removed}
    \end{array} \right.
    \label{eqn:dummyC}
  \end{equation}
\end{linenomath*}
Therefore in both regions, land cover is ``trees" for the period before land cover change and ``removed" for the period after the change. Here we simply assumed that vegetation cover change has occurred on every pixel. The remaining term $\epsilon_r$ is the amount of rainfall that is attributed to other unspecified factors and random errors. Hence the regression model becomes
\vspace{0.5cm}
%\begin{dmath}
\begin{linenomath*}
\begin{equation}
g(E(\mathbf{R}_r)) = \beta'_0 + s'_1(D_{1,r}\mathbf{SOI}) + s'_2(D_{2,r}\mathbf{IOD}) + s'_3\mathbf{Season} + \beta'_1\mathbf{Trend} + \beta'_2\mathbf{LC} + \boldsymbol{\epsilon'}_r
  \label{eqn:model2}
\end{equation}
\end{linenomath*}
Vegetation cover changes occurred at different times in the two regions. In the QLD region, there no exact time can be assigned to the land clearing. Clearing has occurred between 2003 - 2004 according to SLATS reports. The information on the change in type of land cover during this time period is missing. Therefore, four scenarios were tested in the analysis. In these scenarios the ``after change" period started from: (1) June 2003, (2) January 2004, (3) June 2004 and (4) January 2005. In the NSW/VIC region, severe bushfires were reported in early January 2003. Hence the ``tree" cover state was up to December 2002 then it was changed to ``removed" state from January 2003. The regression model was run from 1979 for both regions.

@@

In all regional studies, it is difficult to separate the different influences \citep{CEBON2000211}, and this study also does not capture all the different convergent and divergent effects. The regression model used here is a simple model. We only consider the important effects of historical trend, seasonality and climate drivers. Furthermore, no more than two large scale climatic indices were used in order to avoid over-parameterisation and multiple cross-correlations between climatic indices. A purpose of the regression model is to remove the variability in rainfall that is due to these known important factors. The model shows that seasonality, ENSO and IOD together explain no more than 20\% of the rainfall variability, and around 6 - 8\% on average is due to the climate drivers. This is consistent with the literature \citep[e.g.][]{Westra2010}. A large amount of variation is left in the model residuals, which is likely due to random factors. Rainfall is generally considered a stochastic process \citep[e.g.][]{Fowler2005,Cowpertwait2009,Burton2010}. The high variability increases the difficulty to detect a change in rainfall.

@@

\newpage
%\bibliography
\bibliography{reflist_chap3}

### 2017-11-08 LandSurfaceEffects_LocalRainfall_WRRsubmit.Rnw
add files

\documentclass[authoryear,preprint,review,12pt]{elsarticle}

\journal{Agriculture and Forest Meteorology}

\usepackage{url}
% Elsevier suggests
\usepackage{amssymb}
 \usepackage{lineno}

% older suggested by Chun
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{rotating}
\usepackage{bm}
% french characters
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%switch on line numbers
\linenumbers

\begin{document}
\SweaveOpts{concordance=TRUE}
\begin{frontmatter}

\title{Observational data analysis of land surface effects on local rainfall}

\author{C. Liang}
\author{R.W. Vervoort \corref{cor1}}
\ead{willem.vervoort@sydney.edu.au}
\author{F.F. Van Ogtrop}

\address{Sydney Institute of Agriculture, School of Life and Environmental Sciences, The University of Sydney}
\cortext[cor1]{}

\begin{itemize}
\item There are limited studies that analyse observational data of vegetation feedback on rainfall
\item Two sites with major step trend landuse change were analysed for changes in rainfall
\item Statistical change in rainfall detected after bushfire, but not after land clearing
\end{itemize}

\begin{abstract}
Analysis of observational data to identify relationships between rainfall and land cover change are scarce due to multiple environmental factors that cannot be controlled. In this study we investigated the relationship using statistical methods on data from best available sources at two sites in Australia. Gridded data of rainfall and tree cover were used as spatially corresponding local conditions. Large scale effects were represented by climatic indicators, such as SOI and IOD. Regression analysis and step trend tests were used to assess the effect of abrupt land surface intervention. At a Queensland site, dramatic tree cover change between 2002 - 2005 did not result in strong statistically significant precipitation changes. On the other hand, results from step trend test on 1998 - 2008 rainfall data in a bushfire affected NSW/VIC region has a better match with the tree cover change map. This indicates the method works better when a abrupt change in the data can be clearly identified. The results from the step trend test implied a positive relationship between the tree cover and the rainfall at 0.1 significance level. 
\end{abstract}

\begin{keyword}
Observed data analysis \sep Rainfall change \sep Landcover feedback
\end{keyword}

\end{frontmatter}

@@

Land use and land cover changes can lead to changes in the local climate. Some observational and many modelling studies have found cloud types and rainfall are correlated to large scale vegetation cover changes, such as deforestation in the Amazon and in the Sahel \citep{Chagnon2005,Pinto2009, Wang2009, Mei2010, kucharski_further_2013,pitman_scale_2016} and afforestation in south Israel \citep{Otterman1990, Ben-Gai1998}. In terms of observational studies, using airborne measurement in Western Australia, \citet{Junkermann2009} showed a significantly higher level of aerosols over an agricultural area compared to an adjacent natural vegetation. They suggested that a modification of aerosol concentrations due to deforestation could have contributed to a reduction of local rainfall, as more but smaller rain droplets were observed. \citet{Nair2011} reported from the Bunny Fence Experiment in Western Australia that local land use change altered the synoptic west coast trough dynamics and surface roughness, and this resulted in the observed rainfall decrease. Climate sensitivity to land cover change is also found in eastern Australia \citep{McAlpine2007}.

Rainfall over land is generally influenced by multiple factors as has been shown from multiple simulation studies. Locally, there are two main sources: moisture from advective atmospheric transport; and local evapotranspiration \citep{Eltahir1996,Bosilovich2006,Dirmeyer2009,Gimeno2010}. According to \citet{Trenberth1999}, the contribution of advective moisture partially depends on the availability of external moisture and atmospheric transport. On the longer time scale, such as monthly and annually, large scale atmospheric dynamics are affected by large scale climate drivers. Many studies have reported significant relationships between rainfall in large parts of Australia and the El Ni\~{n}o-Southern Oscillation (ENSO) \citep{Verdon2004,Risbey2009,Speer2011}. ENSO can be used to represent longer term cycles in rainfall data such as drought. On the other hand, local ET is determined by local land surface characteristics. Local land surface characteristics further influence local scale atmospheric dynamics and hence the amount of rainfall, including contribution from both sources. Therefore land surface plays an important role in local rainfall.

@@

Overall the number of observational data studies related to changes to rainfall due to land cover change is limited. This is because there are some fundamental experimental difficulties in both space (where does evaporated water reappear as rainfall?) and in time (how much time does it take for land cover change effects to appear or disappear?). Therefore, the aim of this study is to use observational data at regional scales to investigate the cause and effect relationship between land cover change and local rainfall using empirical evidence. More specifically, we hypothesize that a step change on the land cover on the surface will cause a step change in the rainfall and that this can be identified statistically. To demonstrate the approach and this effect we studied step changes in rainfall at two locations in Queensland and NSW/Victoria where there are possible step changes in land cover change due to land clearing and bushfires based on tree cover data. More specifically,  step changes in rainfall were identified statistically, which were subsequently associated with land cover change through spatial comparison.

@@

%figure 16
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{bt4_qld.pdf}
\caption{Percentage of pixels showing statistically significant positive Z' values (left) and negative Z' values (right) in QLD at  p $<$ 0.1. The histogram shows the distribution of results from 1000 bootstrap resampling of the rainfall time series. The red dot represents the results from the observed data.}
\label{fig:boot_qld}
\end{figure}

%figure 17
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{bt4_nsw.pdf}
\caption{Percentage of pixels showing statistically significant positive Z' values (left) and negative Z' values (right) in NSW/VIC at p $<$ 0.1. The histogram shows the distribution of results from 1000 bootstrap resampling of the rainfall time series. The red dot represents the results from the observed data.}
\label{fig:boot_nsw}
\end{figure}

@@

In this study, we found some observationl data based evidence, although not strong, that vegetation cover change has changed local rainfall. The semi-parametric method and non-parametric method did totally agree on detecting a significant step change in rainfall in the hot dry QLD region where land clearing has occurred. On the other hand, the bushfires in the humid, temperate mountain range in the NSW/VIC region has experienced reduced rainfall. But the dry spell also plays an important role in the results.

Drought has had a pronounced impact on the land surface condition during the study period, leading to significant reduction in vegetation and extreme events such as bushfires. The associated lack of rainfall and high temperatures may mask the step change in the vegetation. Hence, the signal of LCC feedback on rainfall is probably weaker under such regional dry conditions, as the impact of LCC on rainfall is mainly through changes in moisture convergence \citep{Gorgen2006,Pitman2007}.

\section{acknowledgments}
CL was supported by an Australian Postgraduate Award for this work.

@@

\newpage

%\bibliography
\bibliographystyle{elsarticle-harv} 
\bibliography{reflist_chap3}

>>>>

\documentclass[draft,linenumbers]{agujournal}
\draftfalse

\journalname{Water Resource Research}

\usepackage{url}
%\usepackage[]{color}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{rotating}
\usepackage{bm}

\begin{document}
\SweaveOpts{concordance=TRUE}

\title{Empirical study of land surface effects on local rainfall}

\authors{C. Liang \affil{1}, R.W. Vervoort \affil{1}, F.F. Van Ogtrop \affil{1}}

\affiliation{1}{Sydney Institute of Agriculture, School of Life and Environmental Sciences, The University of Sydney}
\correspondingauthor{R.W. Vervoort}{willem.vervoort@sydney.edu.au}

\begin{keypoints}
\item There are few empirical studies of vegetation feedback on rainfall 
\item Two sites with major step trend landuse change were analysed
\item Statistical change in precipitation detected after bushfire
\end{keypoints}

\begin{abstract}
Empirical evidence of correlations between rainfall and land cover change are scarce due to multiple environmental factors that cannot be controlled. In this study we investigated the relationship using statistical methods on data from best available sources at two sites in Australia. Gridded data of rainfall and tree cover were used as spatially corresponding local conditions. Large scale effects were represented by climatic indicators, such as SOI and IOD. Regression analysis and step trend tests were used to assess the effect of abrupt land surface intervention. At a Queensland site, dramatic tree cover change between 2002 - 2005 did not result in strong statistically significant precipitation changes. On the other hand, results from step trend test on 1998 - 2008 rainfall data in a bushfire affected NSW/VIC region has a better match with the tree cover change map. This indicates the method works better when a abrupt change in the data can be clearly identified. The results from the step trend test implied a positive relationship between the tree cover and the rainfall at 0.1 significance level. 
\end{abstract}

@@

Land use and land cover changes can lead to changes in the local climate. Both empirical and modelling studies have found cloud types and rainfall are correlated to large scale vegetation cover changes, such as deforestation in the Amazon and in the Sahel \citep{Chagnon2005,Pinto2009, Wang2009, Mei2010, kucharski_further_2013,pitman_scale_2016} and afforestation in south Israel \citep{Otterman1990, Ben-Gai1998}. Using airborne measurement in Western Australia, \citet{Junkermann2009} showed a significantly higher level of aerosols over an agricultural area compared to an adjacent natural vegetation. They suggested that a modification of aerosol concentrations due to deforestation could have contributed to a reduction of local rainfall, as more but smaller rain droplets were observed. \citet{Nair2011} reported from the Bunny Fence Experiment in Western Australia that local land use change altered the synoptic west coast trough dynamics and surface roughness, and this resulted in the observed rainfall decrease. Climate sensitivity to land cover change is also found in eastern Australia \citep{McAlpine2007}.

Rainfall over land is generally influenced by multiple factors. Locally, there are two main sources: moisture from advective atmospheric transport; and local evapotranspiration \citep{Eltahir1996,Bosilovich2006,Dirmeyer2009,Gimeno2010}. According to \citet{Trenberth1999}, the contribution of advective moisture partially depends on the availability of external moisture and atmospheric transport. On the longer time scale, such as monthly and annually, large scale atmospheric dynamics are affected by large scale climate drivers. Many studies have reported significant relationships between rainfall in large parts of Australia and the El Ni\~{n}o-Southern Oscillation (ENSO) \citep{Verdon2004,Risbey2009,Speer2011}. ENSO can be used to represent longer term cycles in rainfall data such as drought. On the other hand, local ET is determined by local land surface characteristics. Local land surface characteristics further influence local scale atmospheric dynamics and hence the amount of rainfall, including contribution from both sources. Therefore land surface plays an important role in local rainfall.

@@

Overall the number of empirical studies related to changes to rainfall due to land cover change is limited. This is because there are some fundamental experimental difficulties in both space (where does evaporated water reappear as rainfall?) and in time (how much time does it take for land cover change effects to appear or disappear?). Therefore, the aim of this study is to use empirical evidence at regional scales to investigate the cause and effect relationship between land cover change and local rainfall using empirical evidence. More specifically, we hypothesize that a step change on the land cover on the surface will cause a step change in the rainfall and that this can be identified statistically. To demonstrate the approach and this effect we studied step changes in rainfall at two locations in Queensland and NSW/Victoria where there are possible step changes in land cover change due to land clearing and bushfires based on tree cover data. More specifically,  step changes in rainfall were identified statistically, which were subsequently associated with land cover change through spatial comparison.

@@

%figure 16
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{bt4_qld.pdf}
\caption{Percentage of pixels showing statistically significant positive Z' values (left) and negative Z' values (right) in QLD at  p $<$ 0.1. The histogram shows the distribution of results from 1000 bootstrap resampling of the rainfall time series. The red dot represents the results from the observed data.}
\label{fig:boot_qld}
\end{figure}

%figure 17
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{bt4_nsw.pdf}
\caption{Percentage of pixels showing statistically significant positive Z' values (left) and negative Z' values (right) in NSW/VIC at p $<$ 0.1. The histogram shows the distribution of results from 1000 bootstrap resampling of the rainfall time series. The red dot represents the results from the observed data.}
\label{fig:boot_nsw}
\end{figure}

@@

In this study, we found some evidence, although not strong, that vegetation cover change has changed local rainfall. The semi-parametric method and non-parametric method did not reach an agreement on detecting significant step change in rainfall in the hot dry QLD region where land clearing has occurred. On the other hand, the bushfires in the humid temperate mountain range in the NSW/VIC region could have reduced rainfall. But the dry spell also plays an important role in the results.

Drought has had a pronounced impact on the land surface condition during the study period, leading to significant reduction in vegetation and extreme events such as bushfires. The lack of rainfall associated and high temperature may cause a step change in the vegetation. Hence, the signal of LCC feedback on rainfall is probably weaker under such regional dry condition, as the impact of LCC on rainfall is mainly through changes in moisture convergence \citep{Gorgen2006,Pitman2007}.

@@

\newpage
\begin{acknowledgments}
CL was supported by an Australian Postgraduate Award for this work.
\end{acknowledgments}

%\bibliography
\bibliography{reflist_chap3}
